CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2024-01-03 paper.Rmd
Quoting affiliations

---
title: 'CLPFUDatabase: A suite of R packages for energy conversion chain analysis'
tags:
- energy
- exergy
- R
- matrix mathematics
- energy efficiency
authors:
- name: Matthew Kuperus Heun
  orcid: 0000-0002-7438-214X
  affiliation: 1,2
- name: Zeke Marshall
  orcid: 0000-0001-9260-7827
  affiliation: 2
- name: Emmanuel Aramendia
  orcid: 0000-0002-5964-6776
  affiliation: 2
affiliations:
- name: Engineering Department, Calvin University
  index: 1
- name: School of Earth and Environment, University of Leeds
  index: 2
bibliography: paper.bib
output:
  html_document:
    keep_md: yes
---

>>>>

---
title: 'CLPFUDatabase: A suite of R packages for energy conversion chain analysis'
tags:
- energy
- exergy
- R
- matrix mathematics
- energy efficiency
authors:
- name: Matthew Kuperus Heun
  orcid: 0000-0002-7438-214X
  affiliation: "1,2"
- name: Zeke Marshall
  orcid: 0000-0001-9260-7827
  affiliation: 2
- name: Emmanuel Aramendia
  orcid: 0000-0002-5964-6776
  affiliation: 2
affiliations:
- name: Engineering Department, Calvin University
  index: 1
- name: School of Earth and Environment, University of Leeds
  index: 2
bibliography: paper.bib
output:
  html_document:
    keep_md: yes
---
